Building socket-aware BPF programs

### 2018-10-27 paper/paper.tex
paper: Fix up API listing

\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\todo{Span this listing across two columns}
\begin{lstlisting}[caption={BPF API helper functions for socket lookup},language=c,label=lst:helper-api,breaklines=true]
struct bpf_sock *bpf_sk_lookup_tcp(void *ctx, struct bpf_sock_tuple *tuple, u32 tuple_size,
                                   u32 netns, u64 flags)
struct bpf_sock *bpf_sk_lookup_udp(void *ctx, struct bpf_sock_tuple *tuple, u32 tuple_size,
                                   u32 netns, u64 flags)
int bpf_sk_release(struct bpf_sock *sk)
\end{lstlisting}

>>>>

\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}
\begin{filecontents*}{sk-lookup-api.c}
\import{sk-lookup-api.c}
\end{filecontents*}

@@

\lstinputlisting[float=*t,%
  caption={BPF API helper functions for socket lookup},%
  language=c,%
  label=lst:helper-api,%
  breaklines=true]{sk-lookup-api.c}
